### 2020-01-15 overview.tex
some wording

Despite the conceptual simplicity, there are several technical details that require careful treatment in a numerical simulation.
First, due to deformation of the particle or non-uniformity of the flow field, the Lagrangian particles may need to be redistributed, added, or deleted from time to time to ensure numerical stabilty and accuracy.
This is particularly cumbersome when droplets coalesce or breakup.
Second, advection of the marker points requires interpolation of the velocity field, as the moving grid is generally non-aligned with the background fixed mesh.
Third, the internal boundary conditions (no-slip or surface tension) are to be computed on the fixed mesh, thus a ``spreading'' procedure is nessesary to couple the particle and fluid dynamics. This is usually done with a smeared delta function.

@@

\begin{algorithm}[h!]
 \ccc{\footnotesize //time marching} \\
 \For{$n=0,1,\dots,N$}{
  ${\bm u}_{ijk}^0 = {\bm u}_{ijk}^{(n)}$,
  ${\bf RU}_{ijk}^0 = {\bf RU}_{ijk}^{(n)}$, ${\bf RU}_{ijk}^{-1} = {\bf RU}_{ijk}^{0}$  \\
  $\bm{X}^{0}=\bm{X}^{(n)}$, $\bm{U}^{0}=\bm{U}_p^{(n)}+ {\bm \Omega}_p^{(n)} \times \bm{R}$, $\bm{\Omega}_p^{0}=\bm{\Omega}_p^{(n)}$ \\
  $\bm{F}_p^{0}=\bm{F}_p^{(n)}$, $\bm{T}_p^{0}=\bm{T}_p^{(n)}$ \\

@@

    \ccc{\footnotesize //the Lagrangian particle loop} \\
    \For{$l=1,2,\dots,N_l$}{
    $\bm{U}_{l}^{**,s-1} = \sum_{ijk} {\bm u}_{ijk}^{**,s-1} \delta_p( \bm{x}_{ijk}-\bm{X}_{l}^{q-1}) \Delta x \Delta y \Delta z$ \\
    $\bm{F}_{l}^{q-1/2,s} = \bm{F}_{l}^{q-1/2,s-1} + \frac{\bm{U}_{p}(\bm{X}_{l}^{q-1})-\bm{U}_{l}^{**,s-1}}{\Delta t} $ \\
    }

@@

  ${\bm u}_{ijk}^{(n+1)}={\bm u}_{ijk}^3$, ${\bf RU}_{ijk}^{(n+1)}={\bf RU}_{ijk}^3$  \\
  $\bm{X}^{(n+1)}=\bm{X}^{3}$, $\bm{U}_p^{(n+1)}=\bm{U}_p^{3}$, $\bm{\Omega}_p^{(n+1)}=\bm{\Omega}_p^{3}$ \\
  $\bm{F}_p^{(n+1)}=\bm{F}_p^{3}$, $\bm{T}_p^{(n+1)}=\bm{T}_p^{3}$ \\
 }
 \caption{A multi-direct forcing immersed boundary method for the coupled Navier-Stokes/Newton-Euler equations.}
 \label{al:ibm}
\end{algorithm}

@@

The feedback of the particle on the fluid flow are embedded in a diffuse body-forcing term, $\bm f$.
Depending on whether it is incorporated into the continuous equations before or after discretisation, IB methods can be broadly divided into \emph{continuous forcing} and \emph{direct forcing}.
Regardless of the approach, the spreading of the Lagrangian force onto the Euler mesh is realized with regularized Dirac delta functions, which may take different forms and satisfy $\sum_{ijk} \delta_p( \bm{x}_{ijk}-\bm{X}_{l}) \Delta x \Delta y \Delta z=1$ for all $\bm{X}_{l}$.
To illustrate how it can be implemented, a pseudo code correspoinding to the direct forcing IB method for spherical particles using a third-order Runge-Kutta temporal integration is provided in Algorithm \ref{al:ibm}. There, the notation is similar to the previous formulations, cf.\ Eqs. \eqref{eq:projection-method} and \eqref{eq:lagrangian}, except that ${\bf RU}$ does not include $\bm f$; and some terms are simplified or omitted for ease of reading. See \cite{ Wim-Paul_JCP_2012} for the full details.

@@

First we describe three Eulerian methods.
marker functions, boundary conditions (surface tension) \citep{Brackbill_JCP_1992}
Also ghost fluid method.
Figure \ref{fig:front-capture}.

@@

Note that, in the above formulations, the \emph{total} volume of each fluid phase is conserved by construction.
This is the minimum requirement for a long-time simulation to be meaningful and makes VOF appealing in a wide range of industrial problems, such as predicting the impact of ocean waves splashing on the ship hull or designing spray nozzles to enhance fuel mixing in engines.
On the other hand, to correctly capture the local interface motion, the volume flux in Eq.\ \eqref{eq:vof-advect} must be calculated accurately, which requires certain information of the local interface \emph{geometry}, such as the normal direction and curvature.
This further requirement is not straightforward knowing only the cell-averaged volume fraction, therefore, many efforts have been devoted to developing methods that either reconstruct the interface in an extra step (these methods are called geometric VOF) or represent the interface in certain ways such that the volume flux can be computed directly (these methods are called algebraic VOF). See \cite{mirjalili_jain_dodd_2017a} for a recent overview of the different methods.

@@

@@

\section{Effective slip}

>>>>

Despite the conceptual simplicity, there are several technical details that require careful treatment in an implementation.
First, due to deformation of the particle or non-uniformity of the flow field, the Lagrangian particles may need to be redistributed, added, or deleted from time to time to ensure numerical stabilty and accuracy.
This is particularly cumbersome when droplets coalesce or breakup.
Second, advection of the marker points requires interpolation of the velocity field, as the moving grid is generally non-aligned with the background fixed mesh.
Third, the internal boundary conditions (no-slip or surface tension) are to be computed on the fixed mesh, thus a ``spreading'' procedure is nessesary to couple the particle and fluid dynamics. This is usually done with a smeared delta function.

@@

\begin{algorithm}[h!]
 \ccc{\footnotesize //time marching} \\
 \For{$n=0,1,\dots,N$}{
  ${\bm u}_{ijk}^0 = {\bm u}_{ijk}^{(n)}$,
  ${\bf RU}_{ijk}^0 = {\bf RU}_{ijk}^{(n)}$, ${\bf RU}_{ijk}^{-1} = {\bf RU}_{ijk}^{0}$  \\
  $\bm{X}_l^{0}=\bm{X}_l^{(n)}$, $\bm{U}_p^{0}=\bm{U}_p^{(n)}$, $\bm{\Omega}_p^{0}=\bm{\Omega}_p^{(n)}$ \\
  $\bm{F}_p^{0}=\bm{F}_p^{(n)}$, $\bm{T}_p^{0}=\bm{T}_p^{(n)}$ \\

@@

    \ccc{\footnotesize //the Lagrangian particle loop} \\
    \For{$l=1,2,\dots,N_l$}{
    $\bm{U}_{l}^{**,s-1} = \sum_{ijk} {\bm u}_{ijk}^{**,s-1} \delta_p( \bm{x}_{ijk}-\bm{X}_{l}^{q-1}) \Delta x \Delta y \Delta z$ \\
    $\bm{F}_{l}^{q-1/2,s} = \bm{F}_{l}^{q-1/2,s-1} + \frac{\bm{U}_{p}^{q-1}-\bm{U}_{l}^{**,s-1}}{\Delta t} $ \\
    }

@@

  ${\bm u}_{ijk}^{(n+1)}={\bm u}_{ijk}^3$, ${\bf RU}_{ijk}^{(n+1)}={\bf RU}_{ijk}^3$  \\
  $\bm{X}_l^{(n+1)}=\bm{X}_l^{3}$, $\bm{U}_p^{(n+1)}=\bm{U}_p^{3}$, $\bm{\Omega}_p^{(n+1)}=\bm{\Omega}_p^{3}$ \\
  $\bm{F}_p^{(n+1)}=\bm{F}_p^{3}$, $\bm{T}_p^{(n+1)}=\bm{T}_p^{3}$ \\
 }
 \caption{A multi-direct forcing immersed boundary method for the coupled Navier-Stokes/Newton-Euler equations.}
 \label{al:ibm}
\end{algorithm}

@@

The feedback of the particle on the fluid flow are embedded in a diffuse body-forcing term, $\bm f$.
Depending on whether it is incorporated into the continuous equations before or after discretisation, IB methods can be broadly divided into \emph{continuous forcing} and \emph{direct forcing}.
Regardless of the approach, the spreading of the Lagrangian force onto the Eulerian mesh is realized with regularized Dirac delta functions, which may take different forms as long as $\sum_{ijk} \delta_p( \bm{x}_{ijk}-\bm{X}_{l}) \Delta x \Delta y \Delta z=1$ is satisfied for all $\bm{X}_{l}$.
To illustrate the overall algorithm, a pseudo code correspoinding to a direct forcing IB method for spherical particles using a third-order Runge-Kutta temporal integration is provided in Algorithm \ref{al:ibm}. We note that the notation is similar to the previous formulations, cf.\ Eqs. \eqref{eq:projection-method} and \eqref{eq:lagrangian}, except that ${\bf RU}$ does not include $\bm f$; and some terms are simplified or omitted for ease of reading. See \cite{ Wim-Paul_JCP_2012} for the full details.

@@

Instead of meshing and tracking the moving boundary on a separate grid, an alternative approach is to capture the particle motion on the same grid but with an additional function. Such function may correspond to the local volume fraction of a dispersed phase, or measure a geometric quantity at the local position relative to an interface. Conceptually, this is the \emph{Eulerian} specification of a given flow field, and many numerical methods fall under such framework. In the following, we will describe three such methods for ``front-capturing'' (see Figure \ref{fig:front-capture}). A brief historical background will be given first, followed by the definition of the front-capturing function and its governing equation. We will also highlight the major advantages and disadvantages of each method without going into much details. Finally, when coupled with a flow solver, the internal boundary conditions can be treated similarly as in front-tracking methods, cf.\ \eqref{eq:surf-tension}. We skip these details and refer the reader to \cite{Brackbill_JCP_1992, Fedkiw_JCP_1999, Lalanne_JCP_2015, Gibou_Fedkiv_Osher, ICLS} for further details.

@@

Note that, in the above formulations, the \emph{total} volume of each fluid phase is conserved by construction.
This is the minimum requirement for a long-time simulation to be meaningful and makes VOF appealing in a wide range of industrial problems, such as predicting the impact of ocean waves splashing on the ship hull or designing spray nozzles to enhance fuel mixing in engines.
On the other hand, to correctly capture the local interface motion, the volume flux in Eq.\ \eqref{eq:vof-advect} must be calculated accurately, which requires certain information of the local interface \emph{geometry}, such as the normal direction and curvature.
This further requirement is not straightforward knowing only the cell-averaged volume fraction (cf.\ Figure \ref{fig:front-capture}), therefore, many efforts have been devoted to developing methods that either reconstruct the interface in an extra step (these methods are called geometric VOF) or represent the interface in certain ways such that the volume flux can be computed directly (these methods are called algebraic VOF). See \cite{mirjalili_jain_dodd_2017a} for a recent overview of the different methods.

@@

\medskip
In summary...
\lb{add a generic pseudo code for all front-capturing methods.}

@@

\section{Moving contact line}
